Paper 3 - Tables

### 2023-04-06 docs/causal_roadmap.qmd
Started working on dictionaries for variables from DAGs to HELIX data and labels variables from HELIX codebooks. Added info to causal roadmap, including summary diagram of research questions and trinagulation

@@

Using `r I(cv.folds)`-fold \acr{cv}, \acr{sl} builds the best weighted combination of predictions from the algorithms listed in \@ref(tab:lmtp-specs). In case of repeated measures of the exposures, an `ID` variable will be used to make sure that the `r I(cv.folds)`-fold \acr{cv} splits will keep observations from the same individuals in the same split.

@@

* \acr{opps}:
  * The \acr{snps} of the *PON1* (paraoxonase 1) gene, known to influence the ability to metabolize and detoxify \acr{opps}: `rs854560` and `rs662`. Reference: https://doi.org/10.1289/ehp.1408976.
  * The \acr{snps} of the genes coding for \acr{opps}-metabolizing enzymes: `rs1803274`, `rs1799807`, `rs662`, `rs854560`, `rs705379`, `rs4244285`, `rs3892097`, and `rs2177180`. Reference: https://doi.org/10.1016/j.chemosphere.2015.07.079.
* Phenols:
  * The \acr{snp} of the *UGT2B15* gene: `rs1902023`. Reference: https://doi.org/10.1016/j.envint.2020.106172.
* Phthalates:
  *  The \acr{snps} of the cytochrome P450 (*CYPs*) and UDP-glucuronosyltransferase (*UGTs*) genes: `rs1057910`, `rs1799853`, `rs4244285`, `rs12248560`, `rs3892097`, `rs1902023`, and `rs11692021`. Reference: https://doi.org/10.1016/j.envint.2021.107046.
  * The \acr{snps} of the *PPAR*$\alpha$ gene: `rs75525202`, `rs4823902`, `rs4253690`, `rs12330015`, `rs5766698`, `rs115250492`, and `rs1800246.` Reference: https://doi.org/10.3389/fgene.2022.855544. Not sure whether these \acr{snps} should be considered in the list below.

@@

```{r}
#| fig-cap: DAG for research question 3.
#| fig-align: center
#| fig-width: 30
#| fig-height: 40
#| out-extra: "keepaspectratio=true"
```

>>>>

@fig-diagram summarizes the research questions and adopted methods to answer them. In case of regression analysis using \acr{mtps}, the causal quantity of interest, $\phi^{\Delta, i} = \mathbb{E}[Y^{d_i}] - \mathbb{E}[Y]$, will be *adapted* to the research question (i.e., different policies based on the type of exposure).

```{mermaid}
%%| fig-cap: Diagram summarizing research questions and methods.
%%| label: fig-diagram
flowchart LR
  paper[Paper 3] --> rq1("RQ1
                          neuro~chemical")
  paper          --> rq2("RQ2
                          met~chemical")
  paper          --> rq3("RQ3
                          neuro~met")
  rq1            --> rqReg("Observational study.
                            Method: Regression with MTPs.
                            Causal estimand: phi.
                            Uncertainty quantification: bootstrapping.")
  rq1            --> rq1outNeg("Outcome negative control.
                                Method: Regression with GLMs/GAMs.
                                Uncertainty quantification: bootstrapping.")
  rq1            --> rqLit("Literature search")

  rq2            --> rqReg
  rq2            --> rqCrossCohort("Cross-cohort comparison.
                                    Method: Regression with GLMs/GAMs.
                                    Uncertainty quantification: bootstrapping.")
  rq2            --> rqLit

  rq3            --> rqReg
  rq3            --> rqCrossCohort
  rq3            --> rq3mr("Mendelian Randomization.
                            Causal estimand: .")
```

@@

Using `r I(cv.folds)`-fold \acr{cv}, \acr{sl} builds the best weighted combination of predictions from the algorithms listed in @tbl-lmtp-specs. In case of repeated measures of the exposures, an `ID` variable will be used to make sure that the `r I(cv.folds)`-fold \acr{cv} splits will keep observations from the same individuals in the same split.

@@

* \acr{opps}:
  * The \acr{snps} of the *PON1* (paraoxonase 1) gene, known to influence the ability to metabolize and detoxify \acr{opps}: `rs854560` and `rs662`. Reference: https://doi.org/10.1289/ehp.1408976.
  * The \acr{snps} of the genes coding for \acr{opps}-metabolizing enzymes: `rs1803274`, `rs1799807`, `rs662`, `rs854560`, `rs705379`, `rs4244285`, `rs3892097`, and `rs2177180`. Reference: https://doi.org/10.1016/j.chemosphere.2015.07.079.
* Phenols:
  * The \acr{snp} of the *UGT2B15* gene: `rs1902023`. Reference: https://doi.org/10.1016/j.envint.2020.106172.
* Phthalates:
  *  The \acr{snps} of the cytochrome P450 (*CYPs*) and UDP-glucuronosyltransferase (*UGTs*) genes: `rs1057910`, `rs1799853`, `rs4244285`, `rs12248560`, `rs3892097`, `rs1902023`, and `rs11692021`. Reference: https://doi.org/10.1016/j.envint.2021.107046.
  * The \acr{snps} of the *PPAR*$\alpha$ gene: `rs75525202`, `rs4823902`, `rs4253690`, `rs12330015`, `rs5766698`, `rs115250492`, and `rs1800246`. Reference: https://doi.org/10.3389/fgene.2022.855544. Not sure whether these \acr{snps} should be considered in the list below.

@@

```{r}
#| fig-cap: DAG for research question 3.
#| fig-align: center
#| fig-width: 30
#| fig-height: 40
#| out-extra: "keepaspectratio=true"
dag_rq <- dags$marker_to_out
myphd::visualize_dag(dag_rq)
adj_sets <- dagitty::adjustmentSets(x = dag_rq, 
                                    type = type_mas, effect = type_effect)
```

### 2023-04-06 output/paper/figures.qmd
Started working on dictionaries for variables from DAGs to HELIX data and labels variables from HELIX codebooks. Added info to causal roadmap, including summary diagram of research questions and trinagulation

---
title: "Figures"
output:
  bookdown::pdf_document2
---

```{r}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = FALSE, message = FALSE, 
                      cache = TRUE)
```

<!-- ####################################################################### -->
<!-- Workflow -->
```{r}
```
<!-- ####################################################################### -->

>>>>

---
title: "Paper 3 - Figures"
format:
  pdf:
    pdf-engine: pdflatex
    toc: false
    include-in-header:
      - \usepackage{rotating}
      - \usepackage{float}
      - \usepackage{typearea}
link-citations: true
linkcolor: blue
execute:
  echo: false
  warning: false
  error: false
  message: false
editor_options: 
  chunk_output_type: console
project:
  execute_dir: project
---

```{r}
#| include: false
here::i_am("figures.qmd")
source("../../code/ctd.R")
library(tidyverse)
```

<!-- ####################################################################### -->
# CTD Results
<!-- ####################################################################### -->
```{r}
#| label: fig-ctd-res
#| fig.cap: Barplot CTD.
#| fig.height: 10
#| fig.width: 10
path <- "../../results/files/CTD_chem_diseases_1680702221550_05042023.csv"
ctd <- loadCTD(path = path, 
               filter_evidence = TRUE)
plotCTD(ctd)
```

### 2023-04-06 output/paper/manuscript.qmd
Started working on dictionaries for variables from DAGs to HELIX data and labels variables from HELIX codebooks. Added info to causal roadmap, including summary diagram of research questions and trinagulation

---
title: "Paper X"
keywords:
  - Causal Inference
  - Epidemiology
author:
  - name: "Lorenzo Fabbri"
    number: 1
    email: lorenzo.fabbri@isglobal.org
    orcid: 0000-0003-3031-322X
    attributes:
      corresponding: true
    affiliations:
      - ref: isg
      - ref: upf
affiliations:
  - id: isg
    name: ISGlobal
    city: Barcelona
    state: Spain
  - id: upf
    name: UPF
    city: Barcelona
    state: Spain
format:
  pdf:
    pdf-engine: pdflatex
    toc: false
  # docx:
#csl: journal.csl
bibliography: bibliography.bib
link-citations: true
linkcolor: blue
header-includes:
  - \usepackage{setspace}\doublespacing
  - \usepackage[switch, pagewise, running]{lineno}
  - \linenumbers
  - \renewcommand\linenumberfont{\normalfont\small}
  - \usepackage{rotating}
  - \usepackage{float}
abstract: |
 \singlespacing
 **Background**

@@

\twocolumn
\doublespacing
\pagewiselinenumbers

@@

\newpage
\onecolumn
\singlespacing

>>>>

---
metadata-files:
  - ../../../../all_phd/authors.yml
format:
  pdf:
    pdf-engine: pdflatex
    number-sections: true
    toc: false
    include-in-header:
      - \usepackage{rotating}
      - \usepackage{float}
      - \usepackage{typearea}
    pandoc_args:
      - !expr acronymsdown::add_filter()
bibliography: ../../../../PhD.bib
link-citations: true
linkcolor: blue
execute:
  echo: false
  warning: false
  error: false
  message: false
editor_options: 
  chunk_output_type: console
filters:
  - /home/lorenzo/R/x86_64-pc-linux-gnu-library/4.1/acronymsdown/parse-acronyms.lua
  - ../../../../all_phd/scholarly-metadata.lua
  - ../../../../all_phd/author-info-blocks.lua
acronyms:
  fromfile: ../../../../all_phd/acronyms.yml
  insert_links: false
  insert_loa: false
  sorting: alphabetical
abstract: |
 **Background**

@@

```{r}
#| include: false

here::i_am("manuscript.qmd")
source("../../../../all_phd/info_phd.R")
infos <- info_phd()
```

---
title: "`r infos$paper3$title`"
---

@@

\newpage

### 2023-04-06 output/paper/tables.qmd
Started working on dictionaries for variables from DAGs to HELIX data and labels variables from HELIX codebooks. Added info to causal roadmap, including summary diagram of research questions and trinagulation

---
title: "Paper 3 - Tables"
format:
  docx:
    reference-doc: reference_document.docx
  pdf:
    pdf-engine: pdflatex
    number-sections: true
    toc: false
    margin-left: 15mm
    margin-right: 15mm
    margin-bottom: 20mm
    margin-top: 15mm
    include-in-header:
      - \usepackage{rotating}
      - \usepackage{float}
      - \usepackage{typearea}
link-citations: true
linkcolor: blue
execute:
  echo: false
  warning: false
  error: false
  message: false
editor_options: 
  chunk_output_type: console
project:
  execute_dir: project
---

>>>>

---
title: "Paper 3 - Tables"
format:
  docx:
    reference-doc: reference_document.docx
link-citations: true
linkcolor: blue
execute:
  echo: false
  warning: false
  error: false
  message: false
editor_options: 
  chunk_output_type: console
project:
  execute_dir: project
---
